PANCHANGE_data_preprocessing

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
tidying up code and adding respiratory data import chunk

Count for pcl baseline, retrospective, and prepandemic missingness per person
```{r count of people missing a number of items for pcl}
#baseline
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base)
#retrospective
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro)
#pre-pandemic
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan)
```

Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
```{r complete cases only}
all.items <- c(phq.items_prepan,
                phq.items_base,
                phq.items_retro,
                gad.items_prepan,
                gad.items_base,
                gad.items_retro,
                pcl.items_prepan,
                pcl.items_base,
                pcl.items_retro)

@@

Missingness NAs per person - count and percentages
```{r DEM Missingness}
dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq <- rowSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,colnames(dat.no.sex.no.gender.no.age.no.ibd) %in% all.items]))
freq(dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq)

PHQ.cc$miss_pc_total.phq <- PHQ.cc$na.per.person.phq/PHQ.n.items
freq(PHQ.cc$miss_pc_total.phq)
```

Create tidy data on which the exclusion criteria have been applied
```{r Tidy data}
dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.incomplete.questionnaire

@@

The complete rate for sex, gender and age should be 1 now.

@@

>>>>

Count for pcl baseline, retrospective, and prepandemic missingness per person
```{r count of people missing a number of items for pcl}
# baseline
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base)
# retrospective
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro)
# pre-pandemic
table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan)

# rename dataset
dat.no.sex.no.gender.no.age.no.ibd.missingness <- dat.no.sex.no.gender.no.age.no.ibd
```

#Creating "complete cases" datasets  - NOTE THIS PROBABLY WONT BE USED BUT JUST TO GIVE AN IDEA OF COMPLETE CASES NUMBERS. KT. 
Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
```{r complete cases only}
all.items <- c(phq.items_prepan,
                phq.items_base,
                phq.items_retro,
                gad.items_prepan,
                gad.items_base,
                gad.items_retro,
                pcl.items_prepan,
                pcl.items_base,
                pcl.items_retro)

@@

##Create tidy data on which the exclusion criteria have been applied
Complete sex, gender, age and missingness information applied. 
```{r Tidy data}
dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.missingness

@@

@@

#READ IN RESPIRATORY DATA 
```{r read in respiratory data}
